Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-08-03 output/latex/manuscript.tex
fix supplementary figure 11 and add and reference supplementary data 8
table 1: format title with boldface

\begin{table}[h]
\caption{LVs among the top 20 contributors to the prediction of niacin for five cardiovascular diseases. ``Heart attack, angina, stroke or hypertension'' refers to the UK Biobank data-field 6150. GWAS sample size: Atherosclerosis (361,194 in total and 566 cases), Chronic ischaemic heart disease (361,194 in total and 12,769 cases), Heart attack, angina, stroke or hypertension (360,420 in total and 253,565 cases), Ischaemic heart disease/wide definition (361,194 in total and 20,857 cases), High cholesterol/self-reported (361,141 in total and 43,957 cases). \label{tbl:niacin:cardio:top_lvs}}\label{tbl:niacin:cardio:top_lvs}%\tabularnewline
\centering
\begin{tabular}{lll}
\toprule
LV & Cell type & Disease \\
\midrule
LV116 & Immune cells, skin & Atherosclerosis (ICD10 I70) \\
& & Chronic ischaemic heart disease (ICD10 I25) \\
& & Heart attack, angina, stroke or hypertension \\
& & Ischaemic heart disease (wide definition) \\
LV931 & Immune cells & Atherosclerosis (ICD10 I70) \\
& & Heart attack, angina, stroke or hypertension \\
& & Ischaemic heart disease (wide definition) \\
LV246 & Adipose tissue, liver & Atherosclerosis (ICD10 I70) \\
& & High cholesterol (self-reported) \\
& & Ischaemic heart disease (wide definition) \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\hypertarget{fig:sup:crispr:table1}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/table1.png}
\caption{\textbf{Primers for generating illumina libraries.}}\label{fig:sup:crispr:table1}
}
\end{figure}

>>>>

\begin{table}[h]
\caption{\textbf{LVs among the top 20 contributors to the prediction of niacin for five cardiovascular diseases.} ``Heart attack, angina, stroke or hypertension'' refers to the UK Biobank data-field 6150. GWAS sample size: Atherosclerosis (361,194 in total and 566 cases), Chronic ischaemic heart disease (361,194 in total and 12,769 cases), Heart attack, angina, stroke or hypertension (360,420 in total and 253,565 cases), Ischaemic heart disease/wide definition (361,194 in total and 20,857 cases), High cholesterol/self-reported (361,141 in total and 43,957 cases). \label{tbl:niacin:cardio:top_lvs}}\label{tbl:niacin:cardio:top_lvs}%\tabularnewline
\centering
\begin{tabular}{lll}
\toprule
LV & Cell type & Disease \\
\midrule
LV116 & Immune cells, skin & Atherosclerosis (ICD10 I70) \\
& & Chronic ischaemic heart disease (ICD10 I25) \\
& & Heart attack, angina, stroke or hypertension \\
& & Ischaemic heart disease (wide definition) \\
LV931 & Immune cells & Atherosclerosis (ICD10 I70) \\
& & Heart attack, angina, stroke or hypertension \\
& & Ischaemic heart disease (wide definition) \\
LV246 & Adipose tissue, liver & Atherosclerosis (ICD10 I70) \\
& & High cholesterol (self-reported) \\
& & Ischaemic heart disease (wide definition) \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\hypertarget{fig:sup:crispr:table1}{%
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{images/crispr/table1.png}
\caption{\textbf{Primers for generating illumina libraries.} Sequences are provided in a readable format in Supplementary Data 8.}\label{fig:sup:crispr:table1}
}
\end{figure}
